Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Seciton heading floating

@@

Different tasks may have significantly different demands for resources; some may
have deadlines on the scale of seconds while others have deadlines of hours or
days, some may require specialized hardware available on only certain machines,
some may require using the same machines consistently while others can use
different machines at different times, some may have complex constraints on data
locality, etc.

@@

Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences for special resources than DRF, resulting in better performance for the market-based mechanism. DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others.

@@

This paper presented an initial investigation into the possibility of leveraging prices and a market-based mechanism for resource scheduling. We describe a protocol for use in the Mesos cluster scheduler with beneficial theoretical properties. Simulation evaluation shows that our market-based mechanism can perform reasonably in a backwards-compatible mode, where no economic information is provided. 
We also provide theoretical and experimental evidence that our approach can help manage difficulties
resulting from constraints that are unknown to the scheduler.

>>>>

 \makeatletter
  \let\@copyrightspace\relax
   \makeatother

@@

Different tasks may have significantly different demands for resources; some may
have deadlines on the scale of seconds while others have deadlines of hours or
days, some may require specialized hardware available on only certain machines,
some may require using the same machines consistently while others can use
different machines at different times, some may have complex constraints on data
locality, etc. \\

@@

Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences for special resources than DRF, resulting in better performance for the market-based mechanism. DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others.\\

@@

This paper presented an initial investigation into the possibility of leveraging prices and a market-based mechanism for resource scheduling. We describe a protocol for use in the Mesos cluster scheduler with beneficial theoretical properties. Simulation evaluation shows that our market-based mechanism can perform reasonably in a backwards-compatible mode, where no economic information is provided. 
We also provide theoretical and experimental evidence that our approach can help manage difficulties
resulting from constraints that are unknown to the scheduler.\\\\
